How to Avoid OOTA Without Really Trying

### 2025-03-05 paper/ootavacuous.tex
Add Ou and Demsky citation per Reviewer #72A
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Some workers recommend avoiding OOTA by forcing prior relaxed
loads to be ordered before subsequent relaxed
stores~\cite{Boehm:2014:OGA:2618128.2618134,HansBoehm2019OOTArevisitedAgain,Lahav:2017:RSC:3062341.3062352},
but this can require executing real
instructions~\cite[Section 7.1]{Maranget2012TutorialARMPower},
consuming real time and real electrical power to solve a strictly
theoretical problem.
% This might have been acceptable in the 1960s of some of the authors'
% youths, but it is now the year 2024.
Furthermore, as discussed in
Section~\ref{sec:Global Optimization Can Destroy Dependencies},
cross-thread optimizations can defeat this ordering constraint.

@@

All this work focused on either identifying OOTA or helping C++
implementations to avoid it.
None applied real-world hardware ordering constraints to the problem
of avoiding OOTA cycles.
This paper's contribution is to show how these constraints prevent
real-world C++ implementations from exhibiting OOTA behavior.

>>>>

Some workers recommend avoiding OOTA by forcing prior relaxed
loads to be ordered before subsequent relaxed
stores~\cite{Boehm:2014:OGA:2618128.2618134,HansBoehm2019OOTArevisitedAgain,Lahav:2017:RSC:3062341.3062352,PiezhaoOu2018OOTApapl},
but this can require executing real
instructions~\cite[Section 7.1]{Maranget2012TutorialARMPower},
consuming real time and real electrical power to solve a strictly
theoretical problem.
% This might have been acceptable in the 1960s of some of the authors'
% youths, but it is now the year 2024.
Furthermore, as discussed in
Section~\ref{sec:Global Optimization Can Destroy Dependencies},
cross-thread optimizations can defeat this ordering constraint.

@@

All this work focused on either identifying OOTA or helping C++
implementations to avoid it.
None applied real-world hardware ordering constraints to the problem
of avoiding OOTA cycles.
This paper's contribution is to show how these constraints prevent
real-world C++ implementations from exhibiting OOTA behavior, and not with
minimal cost~\cite{PiezhaoOu2018OOTApapl}, but rather with no cost at all.
